\appendix

\section*{Supplemental material}

%===============================%
\section{Rigidity}
\label{sec:rigidity}
%===============================%



\input{rigidity.tex}

%===============================%
\section{The Dog-Walker Protocol}
\label{sec:dog-walker}
%===============================%

\input{dogwalker.tex}

\subsection{Multi-prover game for QMA}\label{sec:qma}

In this section we propose a new multi-prover game for QMA, which is based on the Dog-Walker
protocol.
Recently, there has been an effort to devise such games~\cite{FitzsimonsV15,Ji16,natarajan2016robust},
due to their connections to the quantum PCP conjecture~\cite{AharonovAV13}.


A promise problem $L$ is in QMA if there is a uniform family
of quantum circuits $\{V_x\}_{x \in L}$ such that if $x$ is a yes-instance, then there exists a
quantum state $\ket{\psi} \in \left(\C^2\right)^{\otimes n_w}$, such that
$V_x$  accepts on input $\ket{\psi}\ket{0}^{\otimes n_a}$ with probability at least
$\frac{2}{3}$, while for a no-instance $x$ and  all states $\ket{\psi} \in
\left(\C^2\right)^{\otimes n_w}$, $V_x$
rejects on input $\ket{\psi}\ket{0}^{\otimes n_a}$ with probability at
least $\frac{2}{3}$. The run-time of the circuit $V_x$ and the values $n_w$ and $n_a$ are polynomially bounded in $|x|$.

 In a multi-prover game for a promise problem $L$, an
 instance $x \in L$ is reduced to ja game $G_x$ such that if $x$ is a yes-instance, then the maximum
 acceptance probability in the game is at least $c$, whereas if $x$ is a
 no-instance,
 then the maximum acceptance probability in the game is  at most $s$, for $c
 > s$.

 Here, we are interested in multi-prover games where the verifier is classical,
 the honest provers run a polynomially bounded quantum computation on copies
 of an accepting witness and the completeness-soundness gap $c-s$ is constant.
Using the Dog-Walker protocol, we are able to construct, to the best of our knowledge, the first two-prover
game for QMA with these parameters. In our protocol the Verifier and provers exchange messages of polynomial size 
in two rounds of communication, one with each
prover.

Our protocol consists in the Verifier running the Dog-Walker protocol,
  with the following changes:
  \begin{itemize}
    \item On X-Test rounds (resp.\ $Z$ Test-rounds), the Verifier randomly selects  positions where
      $\pv$ has measured in the $Z$ basis (resp.\ $X$ basis) and sends them to $\pp$. $\pp$ uses the EPR pair halves in these positions as the witness register when he executes the circuit $V_x$.
    \item On Rigidity-Computation rounds, the Verifier
      informs $\pv$ of the halves of EPR pairs that should be used to teleport the witness
      state to $\pp$, and $\pv$ reports the outcomes of the teleportation
      measurements along with the answers for the original Dog-Walker protocol. The Verifier ignores the measurements corresponding to the teleportation and uses the remaining bits to perform the same checks as in the original Dog-Walker protocol.
      \item On EPR-Computation rounds, the Verifier informs $\pp$ of the
      EPR pair halves that should be used as the witness when he performs the circuit $V_x$.  
      The Verifier
      also informs $\pv$ of these positions, who should use them to teleport the witness
      state to $\pp$.  The outcomes of the teleportation      measurements are reported to the Verifier along with the answers for the original Dog-Walker protocol, in order that the Verifier can decrypt the output of the computation.
  \end{itemize}

The full description of the protocol is presented in Figures~\ref{fig:qma-protocol-V}, \ref{fig:qma-protocol-PP} and \ref{fig:qma-protocol-PV}, where the differences to the original Dog-Walker protocol are underlined. We state the result and sketch its proof. 


%----------------%
\begin{figure}[H]
\rule[1ex]{\textwidth}{0.5pt}
\vspace{-20pt}
\justify
Let $x$ be an instance of a language $L \in$ QMA and $V_x$ the associated verification circuit. $V_x$ takes as input  an $n_w$-qubit witness register and an $n_a$-qubit ancilla register. It has $t$ $\sf T$ gates, $t_0$ of which are even and $t-t_0$ are odd (see Section~\ref{sec:EPR-protocol} for the definition of even and odd $\sf T$ gates).

\justify
1. Select a round type \textbf{EPR} or \textbf{Rigidity}, and disjoint sets
  $N^w,N^a, T^0,T^1\subset \{1,\ldots,m\}$ of sizes $n_w$, $n_a$,  $t_0$ and $t-t_0$ respectively. 
\begin{description}
\item[EPR] Choose $\vec{z}$ uniformly at random from $\{0,1\}^t$ and send it,
  along with $\vec{x}$, $N^w$, $N^a$, $T^0$ and $T^1$, to $\pp$. Receive measurement outcomes $\vec{c}\in\{0,1\}^t$ and $c_f\in\{0,1\}$ from $\pp$.
\item[Rigidity] Choose $W'$ according to $\mu(\cdot)$ and send it to $\pp$. Receive $\vec{e}'\in \{0,1\}^m$ from $\pp$. 
\end{description}
2. Select a sub-round type at random from \textbf{Computation}, \textbf{X-Test} or \textbf{Z-Test}. 
\begin{description}
\item[Computation] Based on whether it's an \text{EPR} or a \text{Rigidity} Round:
	\begin{description}
	\item[EPR]
		\begin{enumerate}
		\item[(i)] Send $\vec{x}$, $\vec{z}$, $\vec{c}$ and sets \highlight{$N^w$}, $N^a$, $T^0$
      and $T^1$ to $\pv$, and receive measurement outcomes $\vec{a},\vec{b}\in
        \{0,1\}^{n_w + n_a}$ and $\vec{e}\in\{0,1\}^t$.
		\item[(ii)] Apply the update rules from Table \ref{tab:EPR-key-updates} gate-by-gate to obtain the final $\sf X$ key for the output wire $a_f'$. If $c_f+a_f'\neq 0$, $\sf reject$. 
		\end{enumerate}
	\item[Rigidity (Tomography)]
		\begin{enumerate}
		\item[(i)] Choose uniform random strings $\vec{c},\vec{z}\in\{0,1\}^t$, $\vec{x} \in \{0,1\}^n$ 
      to send to $\pv$, along with \highlight{$N^w$}, $N^a$ and $T$, and receive measurement outcomes $\vec{a}, \vec{b}\in \{0,1\}^{n_w + n_a}$ and $\vec{e}\in\{0,1\}^t$. 
		\item[(ii)]
		From $\vec{x}$, $\vec{c}$, $\vec{z}$, $\vec{a}$, $\vec{b}$ and $\vec{e}$, determine the adaptive measurements $W\in\Sigma^{n+t}$ that $V_{EPR}^0$ would have performed (based on Figure \ref{fig:original-protocol-VEPRr}), and $\sf reject$ if the input-output pairs $(W',\vec{e}')$ and $(N\cup T,(W,\vec{e}))$ do not satisfy the winning criterion for $\tom(\Sigma,n+t,m)$.
		\end{enumerate}
	\end{description}
\item[$X$-Test] Based on whether it's an \text{EPR} or a \text{Rigidity} Round:
\begin{description}
	\item[EPR] 
	\begin{enumerate}
		\item[(i)] Choose $W\in\Sigma^m$ uniformly at random among all strings
      satisfying: $W_i=Z$ for all $i\in \highlight{N^w} \cup N^a$; $W_i=Z$ for all $i\in T^0$; and $W_i\in\{X,Y\}$ for all $i\in T^1$. Send $W$ to $\pv$ and receive measurement results $\vec{e}\in\{0,1\}^m$. Let $(\vec{a},\vec{b})=(\vec{e}_N,0^n)$. 
		\item[(ii)] Apply update rules from Table \ref{tab:EPR-key-updates} gate-by-gate to obtain $\forall i\in [t]$ the $\sf X$ key before the $i$-th $\sf T$ gate is applied, $a_i'$, and the final $\sf X$ key for the output wire, $a_f'$. 
If $\exists i$ s.t.\ the $i$-th $\sf T$ gate is even and $c_i\neq a_i'+e_i$, $\sf reject$. If $c_f+a_f'\neq 0$, $\sf reject$. 
	\end{enumerate}
	\item[Rigidity (Clifford)] Choose ${W}$ according to the marginal conditioned on ${W}'$, $\mu(\cdot|{W}')$. 
	Send ${W}$ to $\pv$ and receive $\vec{e}\in\{0,1\}^m$. Reject if   $({W}',\vec{e}',{W},\vec{e})$ doesn't win $\rigid(\Sigma,m)$. 
\end{description}

\item[$Z$-Test] Based on whether it's an \text{EPR} or a \text{Rigidity} Round:
\begin{description}
	\item[EPR] 
	\begin{enumerate}
		\item[(i)] Choose $W\in\Sigma^m$ uniformly at random among all strings
      satisfying: $W_i=X$ for all $i\in \highlight{N^w} \cup N^a$; $W_i\in\{X,Y\}$ for all $i\in T^0$; and $W_i=Z$ for all $i\in T^1$. Send $W$ to $\pv$ and receive measurement results $\vec{e}\in\{0,1\}^m$. Let $(\vec{a},\vec{b})=(0^n,\vec{e}_N)$.
		\item[(ii)] Apply update rules from Table \ref{tab:EPR-key-updates} gate-by-gate to obtain $\forall i\in [t]$, the $\sf X$ key before the $i$-th $\sf T$ gate is applied, $a_i'$. 
If $\exists i$ s.t.\ the $i$-th $\sf T$ gate is odd and $c_i\neq a_i'+e_i$, $\sf reject$. 
	\end{enumerate}
	\item[Rigidity (Clifford)] Identical to $X$-Test case.
\end{description}
\end{description}
\rule[2ex]{\textwidth}{0.5pt}\vspace{-.5cm}
\caption{QMA Protocol: Verifier's point of view.}\label{fig:qma-protocol-V}
\end{figure}


\begin{figure}[H]
\rule[1ex]{\textwidth}{0.5pt}
\vspace{-20pt}
\begin{enumerate}
  \item If $\pp$ receives a question ${W}'$ from $\ver$ (he is playing $\tom$ or $\rigid$):
\begin{enumerate}
     \item[]  Measure the $m$ qubits in the observable indicated by $W'$ --- for example, if $W'\in\Sigma^m$, for $i\in \{1,\ldots,m\}$, measure the $i$-th qubit in the basis indicated by $W_i'$ --- and report
       the outcomes $\vec{e}'$ to~$\ver$.
\end{enumerate}
\item If $\pp$ receives $\vec{x}, \vec{z}$, and sets $N^w$,$N^a$, $T^0$ and $T^1$ from $\ver$ (he is playing the role of $P_{EPR}$ from the EPR Protocol):
\begin{enumerate}
     \item[] Run  prover $P_{EPR}$ from Figure
       \ref{fig:original-protocol-PEPR} with the $V_x$ as the circuit $Q$, on input $\vec{z}$, \highlight{the $n_w$ qubits in $N^w$ as the witness}, the $n_a$ qubits in 
        $N^a$ as the ancilla, and the $t$ qubits in $T^0\cup T^1$ for $\sf T$ gadgets.
     Report the outputs $\vec{c}\in\{0,1\}^t$ and $c_f\in\{0,1\}$ of $P_{EPR}$  to $\ver$. 
\end{enumerate}
\end{enumerate}
\rule[2ex]{\textwidth}{0.5pt}\vspace{-.5cm}
\caption{QMA Protocol: Honest strategy for $\pp$.}\label{fig:qma-protocol-PP}
\end{figure}


\begin{figure}[H]
\rule[1ex]{\textwidth}{0.5pt}
\vspace{-20pt}
\begin{enumerate}
  \item If $\pv$ receives a question ${W}$ from $\ver$ (he is playing $\rigid$ or an $X$- or $Z$-Test Round):
\begin{enumerate}
     \item[]  Measure the $m$ qubits in the observable indicated by $W$ --- for example, if $W\in \Sigma^m$, for $i\in \{1,\ldots,m\}$, measure the $i$-th qubit in the basis indicated by $W_i$ --- and report the outcomes $\vec{e}$ to $\ver$.
\end{enumerate}

  \item If $\pv$ receives $\vec{x}$, $\vec{z}$, $\vec{c}$ and sets $N^w$, $N^a$, $T^0$ and $T^1$ from $\ver$ (he is playing $\tom$ or a Computation Round):
\begin{enumerate}
  \item[] \highlight{Using the EPR pairs in $N^w$, teleports the witness state
    $\ket{\psi}$ that makes $V_x$ accept with high probability. Let $(\vec{a}_{N^w}, \vec{b}_{N^w})$ be the corresponding
    outcomes of the teleportation measurements.}
  \item[] Measure each qubit in $N^a$ in the $Z$ basis with outcomes $\vec{d}$  and let $(\vec{a}_{N^a},
    \vec{b}_{N^a}) = (\vec{d}, \vec{0} )$ 
	\item[] Run the second step of procedure $V_{EPR}^0$ from Figure
    \ref{fig:original-protocol-VEPRr} with $V_x$ as the circuit $Q$, and the
    values $\vec{c}$, $\vec{z}$, \highlight{the $n_w$ qubits in $N^w$ as the witness}, the $n_a$ qubits in 
        $N^a$ as the ancilla, and the $t$ qubits in $T^0\cup T^1$ for $\sf T$ gadgets. Report the outputs  $\vec{a}$, $\vec{b}$ and $\vec{e}$ of $V_{EPR}^0$ to $\ver$.
\end{enumerate}
\end{enumerate}
\rule[2ex]{\textwidth}{0.5pt}\vspace{-.5cm}
\caption{QMA Protocol: Honest strategy for $\pv$.}\label{fig:qma-protocol-PV}
\end{figure}




\begin{lemma}
There
  exists universal constants $0\leq p_{compl}\leq 1$ and $\Delta >0$ such that the following holds. 
Let $L$ be a language in QMA and $x$ an instance of $L$ such that $n = |x|$. Let  $V_x$ be the
  verification circuit for this instance and $g$ the number of gates in $V_x$
  (in the compiled form as described in Section \ref{sec:prelim}). Then there exists a two-round interactive protocol
between a classical verifier and two entangled provers where the Verifier
sends  $O(n + g)$-bit questions to the provers, the provers answer with $O(n + g)$ bits and the protocol satisfies the following properties.
\begin{description}
\item[Completeness:] If $x$ is a yes-instance, then  there is a strategy for the provers such that the Verifier accepts with probability  at least $p_{compl}$.
\item[Soundness:] If $x$ is a no-instance, then for all strategies of the provers, the Verifier accepts with  probability at most
$p_{sound} = p_{compl} - \Delta$.
\end{description}
\end{lemma}
\begin{proof}[Proof sketch]
The Verifier performs the operations described in Figure~\ref{fig:qma-protocol-V}. 

  The completeness of the protocol is straightforward: if $\pp$ and $\pv$ use the strategy in Figures~\ref{fig:qma-protocol-PP} and \ref{fig:qma-protocol-PV}, respectively, then the Verifier accepts with  high probability.

  The soundness of the protocol follows from the combination of the soundness of the
  Dog-Walker protocol and the soundness of the QMA verification circuit. Along the same lines as 
  Lemmas~\ref{lem:PV-2-PP-4}, \ref{lem:ci-unif} and \ref{lem:PV-34},
  we can show that if
  the acceptance probability in Rigidity-Test, Rigidity-Computation and
  EPR-Test rounds
  is sufficiently high, then there is a strategy where the provers follow the honest
  strategy and the acceptance probability in EPR-Computation round is only slightly
  changed.  
  In the case where the provers are honest in the Rigidity-Test, Rigidity-Computation and EPR-Test rounds, no matter which state is held
  by $\pp$ as witness state, $V_x$ rejects with high probability in the EPR-Computation round, by the
  soundness of the QMA verification circuit.  The proof of soundness can be completed by repeating the
  arguments in Lemma~\ref{lem:dogwalker-soundness}.
\end{proof}



\section{Running our protocols in sequence}
\label{sec:sequential}


In this section, we describe a sequential procedure that, starting from our protocols in Sections \ref{sec:leash} and \ref{sec:dog-walker}, ensures that either the verifier aborts, or she obtains the correct outcome of the computation with probability $99\%$. Moreover, for honest provers, the probability that the procedure aborts is exponentially small in the number of sequential repetitions. Our sequential procedure has a number of rounds which depends on the desired soundness. As long as one only requires amplification of an arbitrarily small, but constant, soundness, to a fixed constant, the number of sequential repetitions remains constant.

To emphasize the importance of having such a sequential procedure, we note that, firstly, the current completeness-soundness gap between acceptance probability on \textit{yes} and \textit{no} instances, for both the leash and the Dog-Walker protocol, is a very small constant. Secondly, if a classical client wishes to employ our protocols to delegate a computation, we need to specify what the client interprets, at the end of the protocol, as the outcome of the delegated computation. The natural approach is to have the verifier interpret $\sf accept$ as a \textit{yes} outcome and $\sf reject$ as a \textit{no} outcome. However, this is not enough, as our security model based on the constant gap between acceptance probability for \textit{yes} and \textit{no} instances means that, while the provers have a low probability of making the verifier accept a \textit{no} instance as a $\textit{yes}$, they can always make the verifier accept a \textit{yes} instance as a \textit{no}, simply by behaving so that they are rejected.

The first point is addressed by running copies of the original protocol in sequence to amplify the completeness-soundness gap. The second point is addressed by having the verifier run the protocol twice: once for the circuit $Q$, and once for the circuit $Q'$ defined by appending an $\sf X$ gate to the output wire of $Q$. If $f:X\rightarrow \{0,1\}$ for some $X\subseteq \{0,1\}^n$ is defined by $f(x)=1$ if $\norm{\Pi_0 Q\ket{x}}^2\geq 2/3$, and $f(x)=0$ if $\norm{\Pi_0 Q\ket{x}}^2\leq 1/3$, i.e.\ $Q$ decides $f$ with bounded error $1/3$, then it is easy to see that $Q'$ decides $1-f$ with bounded error $1/3$. Thus, the verifier will accept $x$ as a \textit{yes} instance of $f$ if the protocol outputs ${\sf accept}$ when running $Q$ on $x$ and outputs $\sf reject$ when running $Q'$ on $x$. The verifier accepts $x$ as a \textit{no} instance of $f$ if the protocol outputs $\sf reject$ when running $Q$ on $x$ and outputs $\sf accept$ when running $Q'$ on $x$. The verifier aborts if she sees $\sf accept$-$\sf accept$ or $\sf reject$-$\sf reject$. 



\subsection{Sequential version of our protocols}

Let $P$ denote either the Verifier-on-a-leash or the Dog-Walker protocol from Sections \ref{sec:leash} and \ref{sec:dog-walker} respectively, and let $c$ and $\Delta$ denote the completeness and completeness-soundness gap. Let $\kappa$ be a security parameter.

\begin{figure}[H]
\rule[1ex]{\textwidth}{0.5pt}
\justify
Protocol $\mbox{Seq}(P,c,\Delta, \kappa)$: Let $(Q,x)$ be the verifier's input. 
\begin{enumerate}
\item The verifier runs $\kappa$ copies of protocol $P$ in sequence on input $(Q,x)$ with $\pp$ and $\pv$. Then she runs $\kappa$ copies in sequence on input $(Q',x)$. 
\item Let $\vec{o}, \vec{\tilde{o}} \in \{0,1\}^{\kappa}$ be such that $o_i = 1$ iff the $i$-th copy on input $(Q,x)$ accepts, and $\tilde{o}_i = 1$ iff the $i$-th copy on input $(Q',x)$ accepts. Let $wt(\vec{o})$ and $wt(\vec{\tilde{o}})$ be their Hamming weights. Then, the verifier accepts $1$ as the outcome of the delegated computation if $wt(\vec{o}) \geq (c- \frac{\Delta}{2}) \cdot \kappa$ and $wt(\vec{\tilde{o}}) < (c- \frac{\Delta}{2}) \cdot \kappa$, and she accepts $0$ as the outcome of the computation if $wt(\vec{o}) < (c- \frac{\Delta}{2})\cdot \kappa$ and $wt(\vec{\tilde{o}}) \geq (c- \frac{\Delta}{2}) \cdot \kappa$. Otherwise the verifier aborts.

\end{enumerate}
\rule[2ex]{\textwidth}{0.5pt}\vspace{-.5cm}
\caption{Sequential version of our protocols} \label{fig: gardenhose-protocol-parallel}
\end{figure}

\noindent We state and prove completeness and soundness for the sequential protocol.

\begin{theorem}
Let $c$ and $\Delta$ be respectively the completeness and completeness-soundness gap of protocol P. On input $(Q,x)$:
\begin{itemize}
\item If the provers are honest, $$ \Pr\big(\mbox{Seq}(P, c, \Delta, \kappa) \mbox{  outputs } f(x)\big) \geq 1 - 2\exp \left(-\frac{\Delta^2\kappa}{2}\right) .$$ 
\item For any cheating provers, $$\Pr\big(\mbox{Seq}(P, c, \Delta, \kappa) \mbox{  outputs } 1-f(x)\big) \leq \exp \left(-\frac{\Delta^2\kappa}{8}\right) .$$
\end{itemize}

\end{theorem}

\begin{proof} We first show completeness. 
Let $s = c- \Delta$ be the soundness of protocol P.
Suppose $f(x) = 1$ (the case $f(x) = 0$ is analogous). If the provers are honest, then the probability that the verifier outputs~$1$~is:
\begin{align*}
\Pr(\mbox{Verifier outputs $1$}) &= \Pr \left(wt(\vec{o}) \geq \left(c - \frac{\Delta}{2}\right)\cdot \kappa \,\, \land \,\, wt(\vec{\tilde{o}}) < \left(c - \frac{\Delta}{2}\right)\cdot \kappa \right)\\
&\geq 1-\Pr \left(wt(\vec{o}) < \left(c - \frac{\Delta}{2}\right)\cdot \kappa \right) - \Pr \left(wt(\vec{\tilde{o}}) \geq \left(c - \frac{\Delta}{2}\right)\cdot \kappa \right) \\
&\geq 1 - 2\exp \left(-\frac{\Delta^2\kappa}{2}\right)
\end{align*}
by Hoeffding's inequality.

Next we show soundness.
Again suppose $f(x) = 1$ (the case $f(x) = 0$ is analogous). Let $W_j$ be an indicator random variable for the event $\tilde{o}_j = 1$, and let $F_j = W_j - s$. Define $X_l = \sum_{j=1}^l F_j$, for $l=1,..,\kappa$. The $F_j$ define a submartingale with $|F_j| \leq 1 \,\, \forall j$. Hence, by Azuma's inequality, for any $\kappa\geq 1$, $\Pr(X_\kappa \geq t) \leq \exp(-\frac{t^2}{2\kappa})$. This implies that 
\begin{equation*}
\Pr \left(\sum_{j=1}^{\kappa} W_j - \kappa \cdot s \geq t \right) = \Pr \left(\sum_{j=1}^{\kappa}F_j \geq t \right) = \Pr \left(X_{\kappa} \geq t \right) \leq \exp\left(-\frac{t^2}{2\kappa}\, \right).
\end{equation*}
Then, for any provers $\pp$ and $\pv$,
\begin{align*}
\Pr(\mbox{Verifier outputs $0$}) &\leq \Pr \Big(wt(\vec{\tilde{o}}) \geq (c - \frac{\Delta}{2})\cdot \kappa \Big) \\
&= \Pr \left(\sum_{j=1}^\kappa W_j \geq (c - \frac{\Delta}{2})\cdot \kappa \right) \\
&= \Pr \left(\sum_{j=1}^{\kappa} W_j - \kappa \cdot s \geq \kappa \cdot \frac{\Delta}{2} \right) \\
&\leq \exp \left(-\frac{\Delta^2\kappa}{8}\right). 
\end{align*}
\end{proof}

